%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Associate Data Scientist} % Job title
    {Vacasa} % Organization
    {Portland, OR} % Location
    {Jul 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working with software engineers to create machine learning models to help with business needs.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Junior Analyst} % Job title
    {} % Organization
    {} % Location
    {Sep 2017 - Jul 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Continuing work from Intern projects}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Analyst Intern} % Job title
    {} % Organization
    {} % Location
    {Jun 2017 - Sep 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Building training set for machine learning model to predict owner churn, identifying gaps in owner data, and identifying indicators to help determine at risk owners.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Bioinformaticist - Selker Lab} % Job title
    {University of Oregon - Institute of Molecular Biology} % Organization
    {Eugene, OR} % Location
    {Oct 2016 - May 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Updated and managed scripts for analysis of ChIP-seq and RNA-seq data.}
        \item {Compared ChIP-seq datasets looking at differences in RNA pol II binding between different strains of n. crassa. Done using various data analysis programs and automated using R and bash scripting.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Scientific Programmer - Harms Lab} % Job title
    {} % Organization
    {} % Location
    {Sep 2015 - May 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a GUI using PyQt5 for python API that analyses isothermal calorimetry (ITC) data. Along with this, wrote documentation for GUI using sphinx on Read the Docs as well as a C extension to calculate the binding polynomial in the API. \newline Repo: https://github.com/harmslab/pytc-gui and https://github.com/harmslab/pytc}
        \item {Developed an extension of a phage display analysis pipeline. Researched and implemented different methods of data clustering. \newline Repo: https://github.com/harmslab/phagedisplay}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
